\chapter*{Preface}
\setheader{Preface}

I started this thesis work with the Distributed Systems department after having previously done my bachelor thesis there. My bachelor thesis was on the concept of decentralized general asset markets that allowed clearance in the order of seconds. I became interested in how decentralized systems can distribute the control and burden of a system to the users of that system.

In my master's, I have specialized in the security of networks and systems. I wanted to use this new knowledge together with my previous experience from my bachelor to do research into topics that solve practical problems.

The origin of this current master thesis work stems from a project within the distributed systems research group called Tribler. The Tribler team focuses on creating disruptive technology that takes the control from central authorities and brings it back to the users. They have created a privacy-focused torrent client using a Tor inspired onion protocol that operates completely without any central control. This system relies on many different components that became tightly integrated and hard to maintain. This led to a more general problem within software engineering which sparked the idea of this thesis.

I want to thank my supervisor, Johan Pouwelse, for his guidance during my thesis. He provided me with helpful feedback during this time to help me improve my work. I would also like to thank the members of the Tribler team for their help and support during the development of the work and understanding the tools created by the lab. In particular, I would like to thank Martijn de Vos, with whom I got the chance to work on a paper during my thesis to test the feasibility of a concept used in this work.

\begin{flushright}
{\makeatletter\itshape
    \@author \\
    Delft, November 2019
\makeatother}
\end{flushright}

